Supplementary Material

### 2024-12-15 manuscript/supplement.qmd
correction in supplement
added example table for agreement metrics
no references in supplement
minor correctioin

*Note that @fig-consort-nsclc results in four shortlisted candidates because both CheckMate017/057 have been both shortlisted and only differ in the squamous versus nonsquamous histological eligibility of the trial population.*

@@

# Supplementary Tables

\addcontentsline{toc}{section}{\protect\numberline{}R package documentation}
\includepdf[pages=-]{encore.io_0.2.0.pdf}

@@

@@

# References {.unnumbered}

::: refs
:::

>>>>

*Note that Supplementary @fig-consort-nsclc results in four shortlisted candidates because both CheckMate017/057 have been both shortlisted and only differ in the squamous versus nonsquamous histological eligibility of the trial population.*

@@

# R package documentation

@@

\includepdf[pages=-]{encore.io_0.2.0.pdf}

@@
